\subsection{Code analysis}

The malicious code was successfully decompiled using JadX, there were quite a lot of elements it was not able to decompile.
However, it seemed like the most important parts were intact. 
The code was obfuscated. The connection between classes was impossible to determine.
However, there were still a lot of useful strings and android interactions.

One of the interesting strings existed in two files, \texttt{sources/d/e/a/b.java} and \texttt{sources/d/c/a/b/a.java}.
The strings contained the domain that requests were being sent to, \texttt{https://api.telegram.org/bot}.
This indicated that the application really was making requests to Telegram.

There was a file that was a lot more interesting, however, \texttt{sources/d/e/a/e.java}.
This file contained a long list of package names, which on a first quick glance looked like package names for popular crypto banking applications.
After some investigating it not only contained crypto banking applications but also regular banking applications and email clients.
It even included Dutch banks such as IGN, ABN AMRO and a few others. 

A list of all the applications in the list can be found in Table \ref{rafael-hackeableapps} included at the end of this section.
Some further investigation indicated that the application was attempting to steal data from these applications and send it somewhere.
It can be assumed that it again sends the data to telegram. However, it was near impossible to find in the code whether this was actually the case.

\newpage
\input{individual/rafael/allbanks.tex}